### 2023-10-10 acronyms/acronyms.tex
acronyms

%%%%%%put this in preamble
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
%%%%%

%%%%% put this in right before draft

@@

@@

\newacronym{ics}{ICS}{Industrial Control Systems}
\newacronym{ies}{IES}{Integrated Energy System}
\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
\newacronym{kmp}{KMP}{key measurement point}

@@

\newacronym{snm}{SNM}{special nuclear material}
\newacronym{mba}{MBA}{material balance area}
\newacronym{nma}{NMA}{nuclear materials accounting}
\newacronym{sei}{SEID}{standard error of the inventory difference}
\newacronym{tru}{TRU}{transuranic element}
\newacronym{des}{DES}{discrete event simulation}
\newacronym{sq}{SQ}{significant quantity}
\newacronym{pyn}{PyNE}{Python for Nuclear Engineering}
\newacronym{haz}{HAZOP}{hazard and operability analysis}
\newacronym{msr}{MSR}{molten salt reactor}
\newacronym{mpt}{MPACT}{Materials Protection, Accounting and Control Technology}
\newacronym{aoo}{AOO}{Anticipated Operational Occurrences}
\newacronym{dbe}{DBE}{Design Basis Events}
\newacronym{bde}{BDBE}{Beyond Design Basis Events}
\newacronym{ies}{IES}{Integrated Energy Systems}
\newacronym{mca}{MC\&A}{Materials Control and Accountability}
\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}

@@

\newacronym{aps}{APS}{Arizona Public Service} 
\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
\newacronym{eia}{EIA}{Energy Information Agency}
\newacronym{epa}{EPA}{Environmental Protection Agency}
\newacronym{hx}{HX}{Heat exchanger} 
\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
\newacronym{mwt}{MWth}{Megawatts thermal energy}
\newacronym{ies}{IES}{Integrated Energy System} 
\newacronym{pv}{PV}{Palo Verde Generating Station} 
\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
\newacronym{ro}{RO}{Reverse Osmosis} 
\newacronym{rom}{ROM}{Reduced Order Model} 
\newacronym{spe}{SPECO}{Specific Exergy Costing} 
\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
\newacronym{ieo}{IESO}{Independent Electricity System Operator}
\newacronym{med}{MED}{Multiple-Effect Distillation}
\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
\newacronym{nf}{NF}{Nanofiltration}
\newacronym{jls}{J}{Joules}
\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
\newacronym{iso}{ISO}{Independent System Operator} 
\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
\newacronym{un}{UN}{United Nations}
\newacronym{ict}{ICT}{Information and communications technologies}
\newacronym{nws}{NWS}{Nuclear Weapons States}
\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
\newacronym{mad}{MAD}{Mutually Assured Destruction}
\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
\newacronym{sq}{SQ}{Significant Quantity}
\newacronym{der}{DER}{Distributed Energy Resource}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}

@@

\newacronym{pfc}{PFC}{Primary Frequency Control}
\newacronym{sfc}{SFC}{Secondary Frequency Control}
\newacronym{ace}{ACE}{Area Control Error}
\newacronym{var}{VAr}{Volt-Amps Reactive}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{nyi}{NYISO}{New York Independent System Operator}
\newacronym{ac}{AC}{Alternating Current}
\newacronym{dc}{DC}{Direct Current}

@@

%%%%%put this in the document where the acronym list will appear - Acronyms is in section format
\printnoidxglossary%[title{}] %removes automated Acronyms title too add custom
%%%%%

>>>>

%put this in preamble
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

@@

\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}

@@

@@

@@

\newacronym{ics}{ICS}{Industrial Control System}
\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator}
\newacronym{rcs}{RCS}{Reactor Cooling System}
\newacronym{nic}{NIC}{Network Interface Card}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{pc}{PCAP}{Packet Capture File}
\newacronym{dc}{DC}{direct-current}
\newacronym{ac}{AC}{alternating-current}
\newacronym{csi}{CSIS}{Center for Strategic \& International Studies}
\newacronym{ste}{STEM}{Science, Technology, Engineering, and Mathematics}
\newacronym{pi}{PI}{Principal Investigator}
\newacronym{ans}{ANS}{American Nuclear Society}
\newacronym{sac}{SACNAS}{Society for the Advancement of Chicanos/Hispanics and Native Americans in Science}
\newacronym{ore}{ORED}{Office of Research and Economic Development}
\newacronym{rfd}{RFD}{Office of Research and Faculty Development}
\newacronym{nbe}{NSBE}{National Society of Black Engineers}
\newacronym{inp}{INPO}{Institute of Nuclear Power Operations}
\newacronym{nan}{NANTeL}{National Academy for Nuclear Training e-Learning}
\newacronym{cda}{CDA}{Critical Digital Assets}
\newacronym{nca}{NCA-CD}{National Center of Excellence in Cyber Defense}
\newacronym{ttx}{TTX}{Tabletop Exercise}
\newacronym{cie}{CIE}{Cyber-Informed Engineering}
\newacronym{aas}{AAS}{Adversary-As-A-Service}

@@

\newacronym{iff}{UIIF}{Idaho Falls Center for Higher Education}
\newacronym{fy}{FY}{Fiscal Year}
%\newacronym{}{}{}

@@

%put this in the document somewhere
\printnoidxglossary
%%%%
